Preregistration

### 2021-04-12 preregistration.Rmd
show checksum

---
title: "Preregistration"
author: "Aaron Peikert"
date: "4/12/2021"
output: html_document
params:
  nsim: 16
  nmin: 100
  nmax: 10000
  nstep: 1000
  seed: 1234
---

@@

```{r checksum}
# compute checksum using md5
checksum <- digest::digest(res_raw, "md5")
if(checksum != "e3b116b36c2a267d0e848e692b76fc1a"){
  warning("Mismatch between original and current simulations!")
}
```

>>>>

---
title: "Preregistration"
author: "Aaron Peikert"
date: "4/12/2021"
output: html_document
params:
  nsim: 1000
  nmin: 100
  nmax: 10000
  nstep: 100
  seed: 1234
---

@@

```{r checksum}
# compute checksum using md5
checksum <- digest::digest(res_raw, "md5")
if(checksum != "e3b116b36c2a267d0e848e692b76fc1a"){
  warning("Mismatch between original and current simulations!
          Checksum now is:\n    ", checksum)
}
```
